Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-18 article.tex
fixed lexi table (removed column of "word"

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \begin{tabular}{@{}llrr@{}}
    \toprule
    \textbf{Concept} & \textbf{Kind} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & WORD & 1321 & 100 \\
    change & WORD & 817 & 62 \\
    climate & WORD & 789 & 60 \\
    disease & WORD & 646 & 49 \\
    change & WORD & 569 & 43 \\
    grapevine & WORD & 565 & 43 \\
    viticulture & WORD & 565 & 43 \\
    soil & WORD & 450 & 34 \\
    plant & WORD & 425 & 32 \\
    different & WORD & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
water & 1321 & 100 \\
change & 817 & 62 \\
climate & 789 & 60 \\
disease & 646 & 49 \\
change & 569 & 43 \\
grapevine & 565 & 43 \\
viticulture & 565 & 43 \\
soil & 450 & 34 \\
plant & 425 & 32 \\
different & 300 & 23 \\ \bottomrule
\end{tabular}
\end{table}
